Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-04-03 code-tests.tex
Add Sod shock tube figure and results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sod Shock Tube}
\label{sec.tests.sodshock}
\red{(Greg)}
Problem type 1.  AMR version.  Tests the hydro.
This is also problem 7.2 in the FLASH method paper.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sod Shock Tube}
\label{sec.tests.sodshock}

We begin the paper test suite with the classic Sod shock tube problem \citep{Sod78}, which provides a good test of a scheme's ability to resolve a clean Riemann problem with clear separation between the three waves, in particular a rarefaction fan, a contact discontinuity and a moderate shock.  In Figure~\ref{fig.sodshocktube}, we show the solution for three of our hydro solves, the spatially third-order PPM, as well as the two second-order Zeus and MUSCL schemes.  We use 100 cells across the domain, which is a relatively standard choice and show solutions both with and without AMR.  Without AMR, it is clear that the PPM scheme produces by far the cleanest solution, with all wave families crisply reproduced.  Zeus and MUSCL produce similar results, with MUSCL doing a slightly better job on the rarefaction fan.  In the figure, we also show the mean absolute deviation from the exact solution, as well as the maximum deviation.  These numbers confirm the qualitative differences noted previously.

We also run the same simulation but with two levels of AMR (using a refinement factor of 2), triggered based on a normalized slope greater than 10\% in the density.  This is a minimal level of refinement, and does not include the rarefaction fan at late times.  The results are shown in the bottom panels of Figure~\ref{fig.sodshocktube}, and the results are much better for all three methods, with much sharper shocks and contact discontinuities, and even a better representation of the rarefaction wave, which is only refined at early times.  Although the results are improved for all methods, the PPM still produces the best result, as shown clearly by the compute error norms, shown again in the figure.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/SodShockTube.eps}
\caption{The density distribution of the classic Sod Shock Tube for three different solvers (from left to right) and with (bottom) and without (top) AMR.  In each case 100 zones are used on the root level and the results are shown at $t=0.25$.  All cells are plotted and color-coded by level (at the time shown, only small region surrounding the contact discontinuity and the shock are refined).  In each panel, we show the exact solution as a solid line and the $L_1$ and $L_\infty$ error norms in the upper right.}
\label{fig.sodshocktube}
\end{center}
\end{figure}
